---
title: "PackageDemo"
author: "Jesse Jennings"
date: "2025-12-3"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{PackageDemo}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(JesseLabPkg)
```

## Package Description

This Package encapsulates a variety of functions from assignments done for MATH 4753 for the purpose of demonstrating them and possibly further use in the future. 

Here I shall demonstrate four of the included functions of the package.


## ntickets function

Compute number of tickets an airline should sell given seat count, show probability,
and target overbook probability

Parameters:
  **N:** integer number of seats on the plane
  **gamma:** probability that the plane is truly overbooked
  **p:** probability that a single purchaser shows up

```{r}
ntickets(N = 400,gamma = 0.02,p = .95)
```

## birthday probability function

Computes the probability of at least two people in a group with size(s) n sharing the same birthday.

Parameters:
  **x:** an integer or numeric vector giving the group size(s)
  
```{r}
birthday(35)
```

## myclt function

Returns a histogram of sample means given a sample size and number of iterations

Parameters:
  **n:** Sample size.
  **iter:** Number of Iterations.
  
```{r}
invisible(myclt(10, 10000))
```

## myncurve Function
This function draws a normal curve and shades the area
between two x-values. It also prints the probability value.

Parameters: 
  **mu:** The mean of the normal distribution.
  **sigma:** The standard deviation of the normal distribution. 
  **a:** The starting x-value for shading.

```{r}
myncurve(mu = 10, sigma = 4, a = 10)
```

